Iterative Reduction: Parsing and Interpreting Code Without Trees

### 2024-12-16 Paper/paper.tex
compiling like i like
adding comments infrastructure

%\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, mathtools}
\usepackage{enumitem}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage[backend=biber]{biblatex}

\addbibresource{paper-bib.bib}

@@

\begin{document}

@@

\section{Introduction}

Nowadays, most programming language interpreters follow the following pipeline (see \cite{dragon})
\begin{enumerate}
    \item Lexing: lexically analyze the input code, separating it into atomic \textit{tokens}.
    \item Parsing: convert the parsed tokens into a \textit{parse tree}: a tree which represents the code according to the language's grammar.
    \item Interpreting: recursively descend the tree and execute the code according to the instructions embedded in the tree.
\end{enumerate}
For example, we can parse the following expression:

@@

The idea of the algorithm is as follows: the input is a stream of tokens, which are indivisible characters in any language.
Given a string of tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ (for readability, tokens are written in boxes), we form rules for combining two tokens.
For example, $\mb{\ttt1}$ and $\mb{\ttt+}$ can be combined together to give a token $\mb{\ttt{1,+}}$.
Then if we follow a token of the form $\mb{\ttt{x,+}}$ with a token of the form $\mb{\ttt y}$, the tokens are combined to form a token $\mb{\ttt{x+y}}$.
So for example:
\[ \mbt{1} \mbt{+} \mbt{2} \mbt{+} \mbt{3} \to \mbt{1,+} \mbt2 \mbt+ \mbt3 \to \mbt{3} \mbt+ \mbt3 \to \mbt{3,+} \mbt3 \to \mbt6 \]
But what about \ttt{1+2*3}?
We'd get
\[ \mbt1 \mbt+ \mbt2 \mbt* \mbt3 \to \mbt{1,+} \mbt2 \mbt* \mbt3 \to \mbt3 \mbt* \mbt3 \to \mbt{3,*} \mbt3 \to \mbt9 \]

@@

\printbibliography

>>>>

%\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, mathtools}
\usepackage{enumitem}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{mdframed}

@@

\newcommand{\yoni}[1]{{\begin{mdframed}[linecolor=red]{\color{red}#1}\end{mdframed}}}
\newcommand{\ari}[1]{{\begin{mdframed}[linecolor=blue]{\color{blue}#1}\end{mdframed}}}
\begin{document}

@@

\section{Introduction}
\yoni{comment}
Nowadays, most programming language interpreters follow the following pipeline (see \cite{dragon})
\begin{enumerate}
    \item Lexing: lexically analyze the input code, separating it into atomic \textit{tokens}.
    \item Parsing: convert the parsed tokens into a \textit{parse tree}: a tree which represents the code according to the language's grammar.
\yoni{comment}
    \item Interpreting: recursively descend the tree and execute the code according to the instructions embedded in the tree.
\end{enumerate}
For example, we can parse the following expression:

@@

The idea of the algorithm is as follows: the input is a stream of tokens, which are indivisible characters in any language.
Given a string of tokens $\mb{\sigma^1}\cdots\mb{\sigma^n}$ (for readability, tokens are written in boxes), we form rules for combining two tokens.
For example, $\mb{\ttt1}$ and $\mb{\ttt+}$ can be combined together to give a token $\mb{\ttt{1,+}}$.
\yoni{comment}
Then if we follow a token of the form $\mb{\ttt{x,+}}$ with a token of the form $\mb{\ttt y}$, the tokens are combined to form a token $\mb{\ttt{x+y}}$.
So for example:
\[ \mbt{1} \mbt{+} \mbt{2} \mbt{+} \mbt{3} \to \mbt{1,+} \mbt2 \mbt+ \mbt3 \to \mbt{3} \mbt+ \mbt3 \to \mbt{3,+} \mbt3 \to \mbt6 \]
But what about \ttt{1+2*3}?
We'd get
\[ \mbt1 \mbt+ \mbt2 \mbt* \mbt3 \to \mbt{1,+} \mbt2 \mbt* \mbt3 \to \mbt3 \mbt* \mbt3 \to \mbt{3,*} \mbt3 \to \mbt9 \]

@@

\bibliographystyle{abbrv}
\bibliography{paper-bib}
